---
title: "Exploratory Data Analysis (EDA):  Mineral Data"
author: 'Fiorello Ieva'
output:
  word_document: default
  html_document:
    df_print: paged
    
always_allow_html: yes
---

```{r Libraries, include = FALSE, warning=FALSE, message=FALSE}
###Load Libraries
library(webshot)
library(CLVTools)
library(logbin)
library(rattle)
library(corrplot)
library(fastDummies)
library(survival)
library(survminer)
library(lubridate)
library(prophet)
#library(urbnmapr)
library(ggpubr)
library(rfm)
library(ggrepel)
library(treemap)
library(rpart.plot)
library(rpart)
library(caret)
library(plotly)
#library(rbokeh)
library(DiagrammeR)
library(crosstalk)
library(MonteCarlo)
library(SCperf)
library(DT)
library(dplyr)
library(qrmtools)
library(TTR)
library(xts)
library(zoo)
library(quantmod)
library(qrmtools)
library(forecastHybrid)
library(forecast)
library(Quandl)
library(ggplot2)
library(ggridges)
library(MASS)
library(GMDH)
library(nnfor)
library(glmnet)
library(stats)
library(keras)
library(xgboost)
library(XBRL)
library(finreportr)
library(reshape2)
library(highcharter)
library(dygraphs)
library(PerformanceAnalytics)
library(purrr)
library(tidyr)
library(openair)
library(tidyverse)
library(wordcloud)
library(arules)
library(arulesViz)
library(officer)
library(lubridate)
library(flextable)
library(statebins)
library(pander)
library(kableExtra)
library(ggridges)
library(ggthemes)
library(survival)
library(survminer)
library(intergraph)
library(chron)
library(pander)
library(summarytools)
library(treemapify)
library(DataExplorer)
library(ggcorrplot)

options(knitr.duplicate.label = "allow")
options(scipen=999)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
options(digits=3)
options(warn = -1)

st_options(plain.ascii = FALSE)

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives better results.
                                            # For other themes, using TRUE might be preferable.

library(knitr)
opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')
st_css()

library(knitr)
knitr::opts_chunk$set(cache =TRUE)


```


```{r EDA2,  echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}


###  Set WD
setwd("C:/Users/Fiore/Documents/r_folder")

#getwd()
#list.files()

### Read
eda_raw   <-readr::read_csv("mrds.csv")
eda_raw <-data.frame(eda_raw)

### ETL
eda_raw <- eda_raw %>% dplyr::select(site_name, latitude, longitude, state, com_type, commod1, commod2, commod3,  prod_size, dev_stat,
                                     ore, gangue)
eda_raw[is.na(eda_raw)] <- 0  #Make NAs Zero



### Set Row Number

eda_raw <-eda_raw %>% mutate(line_number = row_number())

eda_raw %>% dplyr::select(line_number, everything())


```



```{r image,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=10, fig.width=12}
  #Loading magick package
library(magick)
library(curl)
#reading a png image frink image
icon <- image_read("https://www.kcmtoday.com/images/kcm/rsi-01.svg")
icon
```


# Exploratory Data Analysis (EDA)

## Data Model
```{r Tables,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}
 


library(datamodelr)

data_report <-eda_raw
dm_f <- dm_from_data_frames(data_report)
  
  
graph <- dm_create_graph(dm_f, rankdir = "BT", col_attr = c("column", "type"))
dm_render_graph(graph)
```


## Introduce Data From .XLS (STATS)
```{r EDA Introduce,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}
int<-introduce(eda_raw)

FitFlextableToPage <- function(ft, N){
  pgwidth<-N
  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

ft <- flextable(int)
FitFlextableToPage(ft,11)   
```



## Missing Data
```{r EDA Missing,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}
plot_intro(eda_raw)
```



## Feature Exploration
```{r EDA3,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}
plot_missing(eda_raw)

```


## Feature Exploration: Discrete Variables Plot 
```{r DISCRET CAR PLOT,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}
plot_bar(eda_raw)

```



## Feature Exploration: Continous Variable Histograms
```{r CV HIST,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}

plot_histogram(eda_raw)

```


## Feature Exploration: Feature Correlation
```{r ALL Feature CORR,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}

plot_correlation(eda_raw)

```

## Feature Exploration: Unsupervised Learned
```{r PCA ALL,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}

plot_prcomp(eda_raw, maxcat = 5L)

```



## Feature Exploration: States  
```{r State Tree Map,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}



title <-c("State Tree Map")

tmp<-eda_raw %>% dplyr::group_by(state) %>% summarize(count=n()) %>% arrange(desc(count)) 
colnames(tmp)<-c("category", "count")

                           
### Tree Map
treemap(tmp,
            index=c("category"),
            vSize="count",
            type="index",
            palette = "Set1",                        # Select your color palette from the RColorBrewer presets or make your own.
            title=title,                      # Customize your title
            fontsize.title=12,                       # Size of the title
 
)

```






## Feature Exploration: Com Type
```{r com_type Tree Map, out.width='100%', message=FALSE, echo=FALSE}


title <-c("Commodity Type")

tmp<-eda_raw %>% dplyr::group_by(com_type) %>% summarize(count=n()) %>% arrange(desc(count)) 
colnames(tmp)<-c("status", "count")

                           
### Tree Map
treemap(tmp,
            index=c("status"),
            vSize="count",
            type="index",
            palette = "Set1",                        # Select your color palette from the RColorBrewer presets or make your own.
            title=title,                      # Customize your title
            fontsize.title=12,                       # Size of the title
 
)

```


## Feature Exploration: Commodity 1
```{r commod1  Tree Map,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}



title <-c(" Commodity 1")

tmp<-eda_raw %>% dplyr::group_by(commod1) %>% summarize(count=n()) %>% arrange(desc(count)) 
colnames(tmp)<-c("Category", "count")

                           
### Tree Map
treemap(tmp,
            index=c("Category"),
            vSize="count",
            type="index",
            palette = "Set1",                        # Select your color palette from the RColorBrewer presets or make your own.
            title=title,                      # Customize your title
            fontsize.title=12,                       # Size of the title
 
)

```

## Feature Exploration: Ore Types
```{r Ore Types,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}



title <-c("Ore Types")

tmp<-eda_raw %>% group_by(ore) %>% summarize(count=n()) %>% arrange(desc(count)) 
colnames(tmp)<-c("Ore", "count")

                           
### Tree Map
treemap(tmp,
            index=c("Ore"),
            vSize="count",
            type="index",
            palette = "Set1",                        # Select your color palette from the RColorBrewer presets or make your own.
            title=title,                      # Customize your title
            fontsize.title=12,                       # Size of the title
 
)

```


## Feature Exploration: Gangue
```{r Types of Gangue,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}



title <-c("Types of Gangue")

tmp<-eda_raw %>% group_by(gangue) %>% summarize(count=n()) %>% arrange(desc(count)) 
colnames(tmp)<-c("Gangue", "count")

                           
### Tree Map
treemap(tmp,
            index=c("Gangue"),
            vSize="count",
            type="index",
            palette = "Set1",                        # Select your color palette from the RColorBrewer presets or make your own.
            title=title,                      # Customize your title
            fontsize.title=12,                       # Size of the title
 
)

```

## Feature Exploration: Gangue (Filter No Values)
```{r Types of Gangue FO,  echo=FALSE, message=FALSE, warning=FALSE,  fig.height=5, fig.width=9}



title <-c("Types of Gangue With Value")

tmp<-eda_raw %>% group_by(gangue) %>% dplyr::filter(gangue != 0) %>% summarize(count=n()) %>% arrange(desc(count)) 
colnames(tmp)<-c("Gangue", "count")

                           
### Tree Map
treemap(tmp,
            index=c("Gangue"),
            vSize="count",
            type="index",
            palette = "Set1",                        # Select your color palette from the RColorBrewer presets or make your own.
            title=title,                      # Customize your title
            fontsize.title=12,                       # Size of the title
 
)

```






